Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
Meeting notes

\jessiet{Proposed paragraph about calibration to replace \S 2.2}
As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter3]{steinwart2008support}, which only applies when given a discrete target loss.
Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

% vertices
\node[vertex] (consis-ell) at  (-4,3) {Consistency w.r.t. $\ell$};
\node[vertex] (consis-gam) at  (2,3) {Consistency w.r.t. $\gamma$};
\node[vertex] (indir-elic) at  (-4,-3) {Indirect elicitation};
\node[vertex] (d-flats) at  (2,-3) {$d$-flats};
\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) \leq d$};
\node[vertex] (q1-bounds) at (14,3) {$\conscvx$ bounds for Q1};
\node[vertex] (q4-bounds) at (14,-3) {$\conscvx$ bounds for Q4};

@@

\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
%% Bo: resolved on Jun 1, afternoon
%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}

@@

\subsection{Proving the lower bound}

>>>>

\jessiet{Proposed paragraph about calibration to replace \S 2.2}
As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter 3]{steinwart2008support}, which only applies when given a discrete target loss.
Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

% vertices
\node[vertex] (consis-ell) at  (-4,2) {Consistency w.r.t. $\ell$};
\node[vertex] (consis-gam) at  (2,2) {Consistency w.r.t. $\gamma$};
\node[vertex] (indir-elic) at  (-4,-2) {Indirect elicitation};
\node[vertex] (d-flats) at  (2,-2) {$d$-flats};
\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) \leq d$};
\node[vertex] (q1-bounds) at (14,2) {$\conscvx$ bounds for Q1};
\node[vertex] (q4-bounds) at (14,-2) {$\conscvx$ bounds for Q4};

@@

\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
\jessie{Talk about BEP? though less detail than old intro- mention tight bounds for $n = 3$.}

%% Bo: resolved on Jun 1, afternoon
%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}

@@

\subsection{Proving the lower bound for spectral risks}
